rang: Reconstructing reproducible R computing environments with ease

### 2023-02-14 paper/paper.rmd

1. By default, the container building process downloads source packages from CRAN and then compiles them from source. This step depends on the future availability of R packages on CRAN (which is extremely likely to be the case in the near future, given the continous availability since 1997-04-23) [^1]. However, it is possible also to cache (or archive) the source packages now. The archived R packages can then be used instead during the building process.

>>>>

1. By default, the container building process downloads source packages from CRAN and then compiles them from source. This step depends on the future availability of R packages on CRAN (which is extremely likely to be the case in the near future, given the continuous availability since 1997-04-23) [^1]. However, it is also possible to cache (or archive) the source packages now. The archived R packages can then be used instead during the building process.
